Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-09 WSSSPE4_report/WSSSPE4_report.tex
added changes to main report file missing from last commit
changed lightning talks to itemize
fixed formatting for combined figure & table
final formatting changes in survey details, new page for references
adding proceedings to body

\usepackage{color}
\usepackage[table]{xcolor}
\usepackage{dcolumn}
\usepackage{float,caption}
\usepackage{graphicx}

@@

\usepackage{rotating}
\usepackage{caption,subcaption}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage{verbatim}
\usepackage{array,booktabs,multicol,multirow}

@@

\author{Daniel~S.\~Katz$^{(1)}$,
Kyle~E.\~Niemeyer$^{(2)}$,
Sandra~Gesing$^{(3)}$,
Lorraine~Hwang$^{(4)}$,
Alice~Allen$^{(5)}$,
Jean~Salac$^{(6)}$,
Neil~Chue~Hong$^{(7)}$,
Santiago~Nunez-Corrales$^{(8)}$
Anshu~Dubey$^{(9)}$,
R.~Stuart~Geiger$^(10)$,
Jonah~Miller$^{11)}$,
Emily~Chen$^{12)}$,
Wolfgang~Bangerth$^{13)}$,
\\Author order to be determined based on contributions
}

@@

Submissions to WSSSPE4 comprised
20 lightning talks,
4 idea papers,
3 position paper,
5 experience papers,
and
3 demos.
Most of the submissions were accepted, since the goal of WSSSPE is always to
take in as many relevant inputs as possible, and to encourage their authors to
participate in sharing and implementing their ideas.
Specifically,
18 lightning talks,
4 idea papers,
3 position paper,
3 experience papers,
and
3 demos
were accepted.
The papers are discussed in Section~\ref{sec:papers},
and the lightning talks are discussed in Section~\ref{sec:lightning}.

\todo{need to mention/link to the proceedings here.}

@@

\note{by Lorraine and Dan}

@@

Intro and description.
A \textsuperscript{\textasteriskcentered} indicates which author presented the
lightning talk, for those with multiple authors.
\katznote{not sure enum list is right here}
\kylenote{I'm fine with itemize, but they were in a particular order, right?}
\katznote{yes, let's go with itemize, but keep them in the same order}
%
\begin{enumerate}
    \item \textbf{Shoaib Sufi: \emph{The Software Sustainability Institute Fellowship
    programme; supporting the social side of research software}}~\cite{Sufi:2016ws}.
    Description
    %Didn’t want to “preach” to the community, wanted to be integrated with the
    % community, hence the fellows programme. Five attending WSSSPE this year.

@@

\bibliographystyle{vancouver}

>>>>

\usepackage{color}
\usepackage[table]{xcolor}
\usepackage{dcolumn}
\usepackage{caption}
\usepackage{graphicx}

@@

\usepackage{rotating}
\usepackage{caption,subcaption}
\usepackage{float}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage{verbatim}
\usepackage{array,booktabs,multicol,multirow}

@@

\author{Daniel~S.~Katz$^{(1)}$,
Kyle~E.~Niemeyer$^{(2)}$,
Sandra~Gesing$^{(3)}$,
Lorraine~Hwang$^{(4)}$,
Alice~Allen$^{(5)}$,
Jean~Salac$^{(6)}$,
Neil~Chue~Hong$^{(7)}$,
Santiago~Nunez-Corrales$^{(8)}$
Anshu~Dubey$^{(9)}$,
R.~Stuart~Geiger$^(10)$,
Jonah~Miller$^{11)}$,
Emily~Chen$^{12)}$,
Wolfgang~Bangerth$^{13)}$,
\\Author order to be determined based on contributions
}

@@

Submissions to WSSSPE4 comprised
20 lightning talks,
4 idea papers,
3 position paper,
5 experience papers,
and
3 demos.
Most of the submissions were accepted, since the goal of WSSSPE is always to
take in as many relevant inputs as possible, and to encourage their authors to
participate in sharing and implementing their ideas.
Specifically,
18 lightning talks,
4 idea papers,
3 position paper,
3 experience papers,
and
3 demos
were accepted.
The papers are discussed in Section~\ref{sec:papers},
and the lightning talks are discussed in Section~\ref{sec:lightning}.
The paper and lightning talks have been published as a volume in the CEUR Workshop Proceedings~\cite{WSSSPE4-proceedings}.

@@

%\note{by Lorraine and Dan}

@@

Intro and description.
A \textsuperscript{\textasteriskcentered} indicates which author presented the
lightning talk, for those with multiple authors.
%
\begin{itemize}
    \item \textbf{Shoaib Sufi: \emph{The Software Sustainability Institute Fellowship
    programme; supporting the social side of research software}}~\cite{Sufi:2016ws}.
    Description
    %Didn’t want to “preach” to the community, wanted to be integrated with the
    % community, hence the fellows programme. Five attending WSSSPE this year.

@@

\newpage
\bibliographystyle{vancouver}
